Just algae 18S community comparison

### 2019-11-16 code/community_comparison_18s.Rmd
update

barplot <- ggplot(best_assignment_rel_abund, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=best_assignment), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  labs(title="Assignment with unedited genbank downloads",
       fill = "18S taxonomic assigmnent",
       y="Relative abundance out of Chlorophyta reads",
       x="Sample ID (in order of increasing elevation)")
barplot

# desired categories: lump C nivalis in Chloromonas, lump

@@

barplot_select <- ggplot(best_assignment_rel_abund, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=best_assignment), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  labs(title="Assignment with select database",
       fill = "18S taxonomic assigmnent",
       y="Relative abundance out of Chlorophyta reads",
       x="Sample ID (in order of increasing elevation)")
barplot_select

@@

```{r}
ggsave(here("manuscript/figs/18s_algae_rel_abund.png"), plot = barplot)
```

>>>>

# check whats missing from this compared to rbcl

rbcl_sample_ids <- algae_percent_rel_abund %>% distinct(sample_id) %>% pull()
s18_sample_ids <- rel_abund_lumped %>% distinct(sample_id) %>% pull()
setdiff(s18_sample_ids,rbcl_sample_ids)

# add a empty row for gar18.04 (adding it upstream of left joining the field)

## add in empty row for gar18.04
gar4_NA_tibble <- tibble(sample_id="gar18.04",
                         protocol=NA_character_, 
                         asv_id=NA_character_, 
                         n_reads=NA_character_,
                         rel_abund=NA_character_ )

rel_abund_w_gar4 <- algae_percent_rel_abund %>% 
  bind_rows(gar4_NA_tibble)

best_assignment_rel_abund <- rel_abund_w_gar4 %>% 
  # calculate relative abundance per genus
  left_join(taxonomy, by="asv_id") %>% 
  group_by(sample_id, best_assignment) %>% 
  summarise(rel_abund = sum(rel_abund)) %>% 
  ungroup() %>% 
  left_join(field, by="sample_id")

view(best_assignment_rel_abund)

barplot <- ggplot(best_assignment_rel_abund, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=best_assignment), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  labs(title="Assignment with unedited genbank downloads",
       fill = "18S taxonomic assigmnent",
       y="Relative abundance out of Chlorophyta reads",
       x="Sample ID (in order of increasing elevation)")
barplot
```

```{r heatmap_18s, include=FALSE}
# lump categories
rel_abund_lumped <- best_assignment_rel_abund %>% 
  mutate(lumped_best_assignment = case_when(best_assignment=="Sanguina_nivaloides"~"Sanguina nivaloides",
                                     best_assignment %>% str_detect("Chloromonas")~"Chloromonas",
                                     # best_assignment == "Chlorogonium"~"Chlorogonium",
                                     best_assignment=="Koliellaceae"~"Trebouxiophyceae",
                                     TRUE~"Other"))
view(rel_abund_lumped)

assign_ord <- c("Sanguina nivaloides", "Chloromonas","Trebouxiophyceae","Other")

my_theme <- theme(axis.text.x = element_text(angle = 45, hjust = 1))

s18_heatmap <- ggplot(rel_abund_lumped, 
                       aes(x=lumped_best_assignment %>% fct_relevel(assign_ord), 
                           y=alias %>% fct_reorder(elev_m))) +
  geom_tile(aes(alpha=rel_abund, fill=lumped_best_assignment %>% fct_relevel(assign_ord))) +
  labs(x="18S taxonomy", y= "Elevation") +
  scale_alpha(range = c(0.01, 1)) +
  my_theme +
  guides(alpha="none", fill="none")
s18_heatmap

# manually remove the Other bar for G1.4
```

@@

barplot_select <- ggplot(best_assignment_rel_abund, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=best_assignment), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  labs(title="Assignment with select database",
       fill = "18S taxonomic assigmnent",
       y="Relative abundance out of Chlorophyta reads",
       x="Sample ID (in order of increasing elevation)")
barplot_select
```

@@

```{r}
ggsave(here("manuscript/figs/18s_algae_rel_abund.png"), plot = barplot)
saveRDS(s18_heatmap, here("output/s18_heatmap.Rda"))
```
